Democracy, Public Support, and Measurement Uncertainty

### 2021-08-08 paper/dcpo_demsupport.Rmd
update moc

>>>>

In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1996,p52], which has been applied in analyses with latent variables [@Trei2008;@Caughey2018;@K2015].
As @Caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.

\begin{equation}
p(\beta,\theta|w,y, Z) = p(\beta|\theta,w,y)p(\theta|Z).
\end{equation}

where $\theta$ is latent varibles with measurement errors conditional on data Z and a measurement model, $w$ is other predictors without errors, $Z$ is indicators for latent variables $X$, and $y$ is the outcome variable.
In this way, we incorportate uncertainty in measuring predictor $\theta$, and uncertainty in the effects of latent variables $\theta$ and other variables $w$ on outcome variable $y$ [@Treie2008, 215].
To sample from the conditional dentsity and the marginal density in the right side of the equation, we follow iterative Monte Carlo procdure described by @Treier2008, at iteration t,
1. We sample $\theta^{s}$ from its posterior distribution $p(\theta|Z)$ and $y$ from $p(y|Z)$. 
2. For each analysis model, we run the model with $y$, $\theta$, and $w$, and save the coefficient estimates $\beta^{s}$ and variance-covariance matrix of $\beta^{s}$, $V^{s}$, both of which change due to the uncertainty in $\theta^{s}$ and $y^{s}$. 
3. We sample $\tilde{\beta^{t}}$ from the multivariate normal density with mean vector $\beta{s}$ and variance-covariace matrix $V^{s}$.

We incorporate uncertainty for five variables, public support for democracy, liberal democracy, electoral democracy, liberal component index, and corruption perceptions index.
